Music Perception 1: Analysis

### 2021-07-02 analysis/analysis.Rmd
move data folder to the front
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("data", pattern = "csv")
combined <- lapply(data_ls, function(f){
  fread(paste("data/", f, sep = ""), sep = ",")
})
all_data <- do.call(rbind.data.frame, combined)

>>>>

```{r read, include = FALSE}
# read files and combine them
data_ls <- list.files("../data", pattern = "csv")
combined <- lapply(data_ls, function(f){
  fread(paste("../data/", f, sep = ""), sep = ",")
})
all_data <- do.call(rbind.data.frame, combined)
